\pkg{dataMaid}: your assistant for data cleaning in \proglang{R}

### 2017-02-08 latex/article_vol2.tex

All in all, the large role of data cleaning in any data analysts
everyday endeavors is hardly matched in the amount of available
\proglang{R} software solutions. In particular, few packages attempt
to implement systematic, reproducible data cleaning. And while the
available tools attempt to alleviate the ubiquitous ad hoc approach to
data cleaning, they are primarily intended for the data savvy users
and less so for the general researcher with a knowledge about a
specific field and the context of the available data. The
\pkg{dataMaid} package \citep{dataMaid} tries to address this by
providing a framework that both allows for extendable, systematic,
reproducible data cleaning, and summarizing findings for researchers
from other fields such that they can act as human experts when
tracking down potential errors.

>>>>

All in all, the large role of data cleaning in any data analysts
everyday endeavors is hardly matched in the amount of available
\proglang{R} software solutions. In particular, few packages attempt
to implement systematic, reproducible data cleaning. And while the
available tools attempt to alleviate the ubiquitous ad hoc approach to
data cleaning, they are primarily intended for the data savvy users
and less so for the general researcher with a knowledge about a
specific field and the context of the available data. The
\pkg{dataMaid} package \citep{dataMaid} presented here tries to address this by
providing a framework that both allows for extendable, systematic,
reproducible data cleaning, and summarizing findings for researchers
from other fields such that they can act as human experts when
tracking down potential errors.
